Probability Aggregation: Dynamic Hierarchical Modeling of Expert Beliefs in Geopolitical Events

### 2013-08-24 paper.tex
Edits

\section{Geopolitical Data Results}
\label{realData}
\noindent
This section discusses results related to the real-world data described in Section \ref{data}. The goal is to provide application specific insight by discussing the specific research objectives itemized in Section \ref{intro} and also to evaluate the \textit{Sample-Then-Calibrate}-procedure in terms of predictive power and calibration. Before presenting the results two practical matters are discussed.

%These matters must be taken into account when aggregating real-world  probability forecasting data, are discussed.

The first matter regards human experts making probability forecasts of 0.0 or 1.0 even when they are not completely sure of the outcome of the future event. For instance, all the 166 questions in our dataset contained both a zero and a one. Transforming such forecasts into the logit-space yields infinities that are highly influential and cause problems in model estimation. To avoid this, \citet{Ariely00theeffects} suggest changing $p = 0.0$ and $1.0$ to $p = 0.02$ and $0.98$, respectively. This is similar to winsorising which sets the extreme probabilities to a specified percentile of the data (see, e.g., \citet{hastings1947low} for more details on winsorising).  \citet{Geo}, on the other hand, consider only probabilities that fall within a constrained interval, say $[0.001, 0.999]$, and discard the rest. Since this implies ignoring a portion of the data, we decided to adopt the first approach by changing $p = 0.0$ and $1.0$ to $p = 0.01$ and $0.99$, respectively.

The second matter is related to the distribution of the class labels in the dataset. If the set of events that occurred is much larger than the set of events that did not occur (or \textit{vice versa}), the dataset is called \textit{imbalanced}. On such data the model can end up over-focusing on the larger class, and as a result, give very accurate forecast performance over the larger class at the cost of performing poorly over the smaller class (see, e.g., \citet{chen2009learning, wallace2012class}). Fortunately, it is often possible to detect a well-balanced form of the dataset. The first step is to find a partition, $S_0$ and $S_1$, of the question indices, $\{1, 2, \dots, K\}$, such that the equality $\sum_{k \in S_0} T_k  = \sum_{k \in S_1} T_k$ is as closely approximated as possible. This is equivalent to an NP-hard problem known in computer science as the \textit{Partition Problem}:  determine whether a given set of positive integers can be partitioned into two sets such that the sums of the two sets equal to each other (see, e.g., \citet{karmarkar1982differencing, hayes2002easiest}). A simple solution is to use a greedy algorithm, which iterates through the values of $T_k$ in descending order, assigning each $T_k$ to the subset that currently has the smaller sum (see, e.g. \citet{kellerer2004knapsack, gent1996phase} for more details on the Partition Problem). After finding a well-balanced partition, the next step is to assign the class labels such that the labels for the questions in $S_x$ are equal to $x$ with $x = 0$ or $1$. Recall from section \ref{calibration_step} that $Z_k$ represents the event indicator for the event associated with the $k$th question. To define a balanced set of indicators, for all $k \in S_x$, let
\begin{align*}
 \tilde{Z}_k &= x\\
\tilde{p}_{i,t,k} &=  \begin{cases} 
1-p_{i,t,k} & \text{if } Z_k = 1-x\\
p_{i,t,k}& \text{if } Z_k = x 
\end{cases}
\end{align*}
with $i = 1, \dots, I_k$, and $t = 1, \dots, T_k$. The set $\left\{\left(\tilde{Z}_k, \{\tilde{p}_{i,t,k} | i = 1, \dots, I_k, t = 1, \dots, T_k \}\right) \right\}_{k=1}^K$ is a balanced version of the data. 
This procedure was used to balance our real-world dataset both in terms of events and time points. The final output splits the events exactly in half ($|S_0| = |S_1| = 83$) such that number of time points in the first and second halves are 8,737 and 8,738, respectively.

\subsection{Out-of-Sample Forecasting}
\label{forecasting}
This section evaluates the out-of-sample predictive performance of \textit{Sample-Then-Calibrate} against several other probability aggregation procedures. All the models are allowed to utilize a training set before making predictions on an independent testing set. In order to clarify some of the upcoming notation, let $S_{train}$ and $S_{test}$ be index sets that partition the data into training and testing sets of sizes $|S_{train}| = N_{train}$ and $|S_{test}| = 166 - N_{test}$, respectively. This means that the $k$th question is in the training set if and only if $k \in S_{train}$. The competing models are as follows.

\begin{enumerate}
\item \textit{Simple Dynamic Linear Model (SDLM)}. This procedure fixes $\boldsymbol{b} = \boldsymbol{1}$ and $\beta = 1$ in the hierarchical model described in Section \ref{model}. The model then reduces to
\begin{eqnarray*}
\boldsymbol{Y}_{t, k} &=&  X_{t, k} + \boldsymbol{v}_{t, k}  \\
X_{t, k} &=& \gamma_k X_{t-1, k} + w_{t, k},
\end{eqnarray*}
where $X_{t,k}$ is the logit-probability used for prediction. Since this model is not hierarchical, estimates of the hidden process can be obtained directly for the questions in the testing set without fitting the model first on the training set. In order to make predictions, the sampler is run for 500 iterations of which the first 200 are used for burn-in. The remaining sample of 300 iterations is thinned by discarding every other observation, leaving a final predictive sample of 150 observations.

\item \textit{The Sample-Then-Calibrate procedure both under the Brier (STC-Bri) and the logarithmic score (STC-Log)}. The model is first fit on the training set by running the sampling step for 3,000 iterations of which the first 500 iterations are used for burn-in. After thinning by only keeping every fifth observation, the calibration step is performed for each of the remaining 500 observations. The out-of-sample prediction is done by running the sampling step for 500 iterations with each consecutive iteration reading in and conditioning on the next value of $\beta$ and $\boldsymbol{b}$ that were found during training period. The first 200 observations are used for burn-in. The remaining sample of 300 iterations is thinned by discarding every other observation, leaving a final predictive sample of 150 observations.

\item \textit{A fully Bayesian version of STC-Log (BSTC-Log)}. Denote the (constrained) calibrated logit-probabilities and  the event indicators across all $K$ questions with $\boldsymbol{X}(1)$ and $\boldsymbol{Z}$, respectively.  The posterior distribution of $\beta$ conditional on $\boldsymbol{X}(1)$ is then given by $p(\beta | \boldsymbol{X}(1), \boldsymbol{Z}) \propto p( \boldsymbol{Z} | \beta, \boldsymbol{X}(1)) p(\beta | \boldsymbol{X}(1))$. Recall that the calibration step under $S_{LOG}$ is equivalent to fitting a logistic regression model with $Z_k$ as the response and $\hat{X}_{k,t}(1)$ as the explanatory variable. Therefore the likelihood for the Bayesian version is
\begin{eqnarray}
p( \boldsymbol{Z} | \beta, \boldsymbol{X}(1)) &\propto& \prod_{k=1}^K \prod_{t=1}^{T_k}  \logit^{-1} \left(X_{k,t}(1)/\beta  \right)^{Z_k} \left( 1-  \logit^{-1} \left( X_{k,t}(1)/\beta  \right) \right)^{1-Z_k} \label{OSE2}
\end{eqnarray}
Similarly to  \citet{gelman2003bayesian} the prior is chosen to be locally uniform, $p(1/\beta) \propto 1$. Posterior estimates of $\beta$ can be sampled from Equation (\ref{OSE2}) using generic sampling algorithms such as the Metropolis algorithm (\citet{metropolis1953equation}) or slice sampling (\citet{neal2003slice}). Since the sampling procedure conditions on the event indicators, the full conditional distribution of the hidden states is a non-standard form. Therefore the Metropolis algorithm is also used for sampling the hidden states. Predictions are made with the same choices of thinning and burn-in as described under \textit{Sample-Then-Calibrate}.

@@

\item  \textit{Exponentially Weighted Moving Beta-transformed Aggregator (EWMBA)}. The static version of the Beta-transformed (linear) aggregator was introduced in \cite{Ranjan08}. A dynamic version can be obtained by replacing $G_{t,k}(\nu )$ in the EWMLA description with
\begin{eqnarray*}
H_{\nu, \tau} \left( \bar{p}_{t,k}\right),
\end{eqnarray*}
where $H_{\nu, \tau}$ is the cumulative distribution function of the Beta distribution and $\bar{p}_{t,k}$ is the average probability forecast defined under EWMA. The tuning parameters $(\alpha, \nu, \tau)$ are learned from the training set by
\begin{eqnarray*}
(\hat{\alpha}, \hat{\nu}, \hat{\tau}) &=& \argmin_{\nu, \tau > 0\ \alpha \in [0,1]} \sum_{k \in S_{train}} \sum_{t=1}^{T_k} \left(Z_k - \hat{p}_{t,k}(\alpha, \nu, \tau)\right)^2
\end{eqnarray*}

@@

Table \ref{prediction} summarizes different ways to aggregate these scores: The first option, denoted by \textit{Scores by Day}, weighs the questions by the number of days the question remained open. This is performed by computing the average of the 17,475 scores. The second option, denoted by \textit{Scores by Problem}, gives each question an equal weight regardless how long the question remained open. This is done by first averaging the scores within a question, and then averaging the average scores across all the questions. Both scores can be further broken down into subcategories by considering the length of the questions. The questions are divided into \textit{Short} questions (30 days or fewer), \textit{Medium} questions (between 31 and 59 days), and \textit{Long} Problems (60 days or more). The number of questions in these subcategories were 36, 32 and 98, respectively. The bolded scores indicate the lowest score in each column. The values in the parenthesis quantify the variability in the scores: Under \textit{Scores by Day} the values give the standard errors of all the scores. Under \textit{Scores by Problem}, on other hand, the values represent the standard errors of the average scores across the questions.

\begin{table}[htbp]
   \centering
      \begin{tabular}{l llll} % Column formatting, @{} suppresses leading/trailing space
 \multicolumn{5}{ c }{Scores by Day}\\
Model & \multicolumn{1}{ c }{All Problems} & \multicolumn{1}{ c }{Short} & \multicolumn{1}{ c }{Medium} & \multicolumn{1}{ c }{Long}\\ \hline
SDLM & 0.100 (0.156) & 0.066 (0.116) & 0.098 (0.154) & 0.102 (0.157)\\ 
BSTC-Log & 0.097 (0.213) & \textbf{0.053} (0.147) & 0.100 (0.215) & 0.098 (0.215)\\ 
STC-Bri & 0.096 (0.190) & 0.056 (0.134) & 0.097 (0.190) & 0.098 (0.192)\\ 
STC-Log & \textbf{0.096} (0.191) & 0.056 (0.134) & \textbf{0.096} (0.189) & \textbf{0.098} (0.193)\\ 
EWMBA & 0.102 (0.203) & 0.060 (0.124) & 0.110 (0.201) & 0.103 (0.206)\\ 
EWMLA & 0.102 (0.199) & 0.061 (0.130) & 0.111 (0.214) & 0.103 (0.200)\\ 
EWMA & 0.111 (0.142) & 0.089 (0.100) & 0.111 (0.136) & 0.112 (0.144)\\ 
&&&&\\
\multicolumn{5}{ c }{Scores by Problem}\\
Model & \multicolumn{1}{ c }{All Problems} & \multicolumn{1}{ c }{Short} & \multicolumn{1}{ c }{Medium} & \multicolumn{1}{ c }{Long}\\ \hline
SDLM & 0.089 (0.116) & 0.064 (0.085) & 0.106 (0.141) & 0.092 (0.117)\\ 
BSTC-Log & 0.083 (0.160) & \textbf{0.052} (0.103) & 0.110 (0.198) & 0.085 (0.162)\\ 
STC-Bri & 0.083 (0.142) & 0.055 (0.096) & 0.106 (0.174) & 0.085 (0.144)\\ 
STC-Log & \textbf{0.082} (0.142) & 0.055 (0.096) & \textbf{0.105} (0.174) & \textbf{0.085} (0.144)\\ 
EWMBA & 0.090 (0.156) & 0.063 (0.101) & 0.118 (0.186) & 0.091 (0.161)\\ 
EWMLA & 0.090 (0.159) & 0.064 (0.109) & 0.120 (0.200) & 0.090 (0.159)\\ 
EWMA & 0.104 (0.105) & 0.092 (0.081) & 0.119 (0.125) & 0.103 (0.107)\\ 
   \end{tabular}
   \caption{Brier Scores based on 10-fold cross-validation. \textit{Scores by Day} weighs a question by the number of days the question remained open. \textit{Scores by Problem} gives each question an equal weight regardless how long the question remained open. The bolded values indicate the lowest scores in each column. The values in the parenthesis represent standard errors in the scores. }
   \label{prediction}
\end{table}

Overall, STC-Bri and STC-Log achieve the lowest average scores across all columns except \textit{Short} where they are slightly outperformed by BSTC-Log.  BSTC-Log, however, turns out to be overconfident (see Section \ref{calibration} with a discussion on calibration and sharpness). This means that BSTC-Log underestimates the uncertainty in the events and outputs probability forecasts that are typically too near 0.0 or 1.0 to be calibrated. As a result, the forecasts are either very close to the correct answer or very far from it.  As can be seen in Table \ref{prediction}, this results into high variance in performance of BSTC-Log. The short questions, however, involve very little uncertainty and were generally the easiest to forecast. On such easy questions, overconfidence can pay off frequently enough to compensate for the few potential large scores that arise from an overconfident and incorrect forecast. In contrast to the BSTC-Log-model, SDLM lacks sharpness and is highly under-confident. This means that SDLM makes conservative forecasts that result into low average scores and low performance variability. The \textit{Sample-Then-Calibrate}-model can therefore be viewed as a well-performing compromise that avoids over-confidence without being too conservative.

 Of the exponentially weighted moving aggregators, EWMBA performs the best and EWMA the worst. Given that the static versions of EWMLA and EWMBA depend on similar transformations, the results suggest that EWMLA is unable to make efficient use of the self-rated expertise information. Both EWMLA and EWMBA, however, suffer from over-confidence and are therefore unable to outperform the \textit{Sample-Then-Calibrate}-model.

The dataset contained a few long questions with an abrupt change of the crowd belief from one answer option to another. Since these abrupt changes happened generally towards the end of each question, during most days the Brier scores were really high. Given that these problems were typically very long, they gained a higher weight under \textit{Scores by Day} than under \textit{Scores by Problem}. This explains why the \textit{Scores by Day} are higher than the \textit{Scores by Problem} under the columns \textit{All Problems} and \textit{Long}.

\subsection{In- and Out-of-Sample Sharpness and Calibration}
\label{calibration}
A calibration plot is a simple tool for assessing the sharpness and calibration of a model. The idea is to plot the probability forecasts against the observed empirical frequencies. Therefore any deviation from the diagonal line suggest poor calibration. A model is considered under-confident (or over-confidence) if the points form an S-shaped (or \reflectbox{S}-shaped) trend. In order to assess sharpness of the model, it is common practice to place a histogram of the given forecasts within the plot.

@@

The top and bottom rows of Figure \ref{Calibration-Out} present calibration plots for SDLM, STC-Log, STC-Bri, and BSTC-Log under in- and out-of-sample probability estimation, respectively. Each case is of interest in its own right:  Good in-sample calibration is crucial for model interpretability. In particular, if the estimated crowd belief is well-calibrated, then the elements of the bias vector $\boldsymbol{b}$ can be used to study the amount of under- or over-confidence in the different expertise groups. Good out-of-sample calibration and sharpness, on other hand, are necessary properties in predicting future events with high accuracy.  To guide our assessment, the dashed bands around the diagonal connect the point-wise, Bonferroni-corrected (\citet{bonferroni}) 95\% lower and upper critical values under the null hypothesis of calibration. These have been computed by running the bootstrap technique described in \citet{brocker2007increasing} for 10,000 iterations. The in-sample results were obtained by running the models were for 10,200 iterations leading to a final posterior sample of 1,000 observations after thinning and using the first 200 iterations for burn-in. The out-of-sample results were computed based on the 10-fold cross-validation discussed in Section \ref{forecasting}.

Overall, the \textit{Sample-Then-Calibrate}-procedure is sharp and well-calibrated both in- and out-of-sample with only a few points barely falling outside the \textit{point-wise} critical values. Since the calibration does not change drastically from the top to the bottom row, the \textit{Sample-Then-Calibrate}-procedure can be considered to present robustness against over-fitting. This is, however, not the case with BSTC-Log that is well-calibrated in-sample but presents over-confidence out-of-sample. Figures \ref{CalibrationNONEa} and \ref{CalibrationNONEb} serve as baselines by showing the reliability plots for the SDLM-model. Since this model does not perform any explicit calibration, it is not surprising to see most points outside the critical values. The pattern in the deviations suggests drastic under-confidence, and the inset histogram reveals drastic lack of sharpness.

>>>>

\section{Geopolitical Data Results}
\label{realData}
\noindent
This section discusses results related to the real-world data described in Section \ref{data}. The goal is to provide application specific insight by discussing the specific research objectives itemized in Section \ref{intro} and also to evaluate the \textit{Sample-Then-Calibrate}-procedure in terms of predictive power and calibration. Before presenting the results, however, we discuss two practical matters that must be taken into account when aggregating real-world  probability forecasts.

\subsection{Incoherent and Imbalanced Data}
The first matter regards human experts making probability forecasts of 0.0 or 1.0 even if they are not completely sure of the outcome of the event. For instance, all the 166 questions in our dataset contained both a zero and a one. Transforming such forecasts into the logit-space yields infinities that are highly influential and cause problems in model estimation. To avoid this, \citet{Ariely00theeffects} suggest changing $p = 0.0$ and $1.0$ to $p = 0.02$ and $0.98$, respectively. This is similar to \textit{winsorising} that sets the extreme probabilities to a specified percentile of the data (see, e.g., \citet{hastings1947low} for more details on winsorising).  \citet{Geo}, on the other hand, consider only probabilities that fall within a constrained interval, say $[0.001, 0.999]$, and discard the rest. Since this implies ignoring a portion of the data, we have decided to adopt the first approach by changing $p = 0.0$ and $1.0$ to $p = 0.01$ and $0.99$, respectively.

The second matter is related to the distribution of the class labels in the data. If the set of occurred events is much larger than the set of events that did not occur (or \textit{vice versa}), the dataset is called \textit{imbalanced}. On such data the modeling procedure can end up over-focusing on the larger class, and as a result, give very accurate forecast performance over the larger class at the cost of performing poorly over the smaller class (see, e.g., \citet{chen2009learning, wallace2012class}). Fortunately, it is often possible to use a well-balanced version of the data. The first step is to find a partition, $S_0$ and $S_1$, of the question indices, $\{1, 2, \dots, K\}$, such that the equality $\sum_{k \in S_0} T_k  = \sum_{k \in S_1} T_k$ is as closely approximated as possible. This is equivalent to an NP-hard problem known in computer science as the \textit{Partition Problem}:  determine whether a given set of positive integers can be partitioned into two sets such that the sums of the two sets equal to each other (see, e.g., \citet{karmarkar1982differencing, hayes2002easiest}). A simple solution is to use a greedy algorithm, which iterates through the values of $T_k$ in descending order, assigning each $T_k$ to the subset that currently has the smaller sum (see, e.g. \citet{kellerer2004knapsack, gent1996phase} for more details on the Partition Problem). After finding a well-balanced partition, the next step is to assign the class labels such that the labels for the questions in $S_x$ are equal to $x$ with $x = 0$ or $1$. Recall from section \ref{calibration_step} that $Z_k$ represents the event indicator for the event associated with the $k$th question. To define a balanced set of indicators, $ \tilde{Z}_k$ for all $k \in S_x$, let
\begin{align*}
 \tilde{Z}_k &= x\\
\tilde{p}_{i,t,k} &=  \begin{cases} 
1-p_{i,t,k} & \text{if } Z_k = 1-x\\
p_{i,t,k}& \text{if } Z_k = x 
\end{cases}
\end{align*}
with $i = 1, \dots, I_k$, and $t = 1, \dots, T_k$. The resulting set $$\left\{\left(\tilde{Z}_k, \{\tilde{p}_{i,t,k} | i = 1, \dots, I_k, t = 1, \dots, T_k \}\right) \right\}_{k=1}^K$$ is a balanced version of the data. 
This procedure was used to balance our real-world dataset both in terms of events and time points. The final output splits the events exactly in half ($|S_0| = |S_1| = 83$) such that number of time points in the first and second halves are 8,737 and 8,738, respectively.

\subsection{Out-of-Sample Forecasting}
\label{forecasting}
This section evaluates the out-of-sample predictive performance of \textit{Sample-Then-Calibrate} against several other probability aggregation procedures. The models are allowed to utilize a training set before making predictions on an independent testing set. In order to clarify some of the upcoming notation, let $S_{train}$ and $S_{test}$ be index sets that partition the data into training and testing sets of sizes $|S_{train}| = N_{train}$ and $|S_{test}| = 166 - N_{test}$, respectively. This means that the $k$th question is in the training set if and only if $k \in S_{train}$. The competing models are as follows.

\begin{enumerate}
\item \textit{Simple Dynamic Linear Model (SDLM)}. This is equivalent to the dynamic model from Section \ref{model} but with $\boldsymbol{b} = \boldsymbol{1}$ and $\beta = 1$. Thus,
\begin{eqnarray*}
\boldsymbol{Y}_{t, k} &=&  X_{t, k} + \boldsymbol{v}_{t, k}  \\
X_{t, k} &=& \gamma_k X_{t-1, k} + w_{t, k},
\end{eqnarray*}
where $X_{t,k}$ is the logit-probability used for prediction. Since this model is not hierarchical, estimates of the hidden process can be obtained directly for the questions in the testing set without fitting the model first on the training set. In order to make predictions, the sampler is run for 500 iterations of which the first 200 are used for burn-in. The remaining 300 iterations is thinned by discarding every other observation, leaving a final predictive sample of 150 observations.

\item \textit{The Sample-Then-Calibrate procedure both under the Brier (STC-Bri) and the logarithmic score (STC-Log)}. The model is first fit on the training set by running the sampling step for 3,000 iterations of which the first 500 iterations are used for burn-in. After thinning by only keeping every fifth observation, the calibration step is performed for the remaining 500 observations. The out-of-sample prediction is done by running the sampling step for 500 iterations with each consecutive iteration reading in and conditioning on the next value of $\beta$ and $\boldsymbol{b}$ that were found during the training period. The first 200 iterations are used for burn-in. The remaining 300 iterations are thinned by discarding every other observation, leaving a final predictive sample of 150 observations.

\item \textit{A fully Bayesian version of STC-Log (BSTC-Log)}. Denote the (constrained) calibrated logit-probabilities and  the event indicators across all $K$ questions with $\boldsymbol{X}(1)$ and $\boldsymbol{Z}$, respectively.  The posterior distribution of $\beta$ conditional on $\boldsymbol{X}(1)$ is then given by $p(\beta | \boldsymbol{X}(1), \boldsymbol{Z}) \propto p( \boldsymbol{Z} | \beta, \boldsymbol{X}(1)) p(\beta | \boldsymbol{X}(1))$. Recall that the calibration step under $S_{LOG}$ is equivalent to fitting a logistic regression model with $Z_k$ as the response and $\hat{X}_{k,t}(1)$ as the explanatory variable. Therefore the likelihood for the Bayesian version is
\begin{eqnarray}
p( \boldsymbol{Z} | \beta, \boldsymbol{X}(1)) &\propto& \prod_{k=1}^K \prod_{t=1}^{T_k}  \logit^{-1} \left(X_{k,t}(1)/\beta  \right)^{Z_k} \left( 1-  \logit^{-1} \left( X_{k,t}(1)/\beta  \right) \right)^{1-Z_k} \label{OSE2}
\end{eqnarray}
Similarly to  \citet{gelman2003bayesian}, the prior is chosen to be locally uniform, $p(1/\beta) \propto 1$. Posterior estimates of $\beta$ can be sampled from Equation (\ref{OSE2}) using generic sampling algorithms such as the Metropolis algorithm (\citet{metropolis1953equation}) or slice sampling (\citet{neal2003slice}). Since the sampling procedure conditions on the event indicators, the full conditional distribution of the hidden states is not in a standard form. Therefore the Metropolis algorithm is also used for sampling the hidden states. Predictions are made with the same choices of thinning and burn-in as described under \textit{Sample-Then-Calibrate}.

@@

\item  \textit{Exponentially Weighted Moving Beta-transformed Aggregator (EWMBA)}. The static version of the Beta-transformed  aggregator was introduced in \cite{Ranjan08}. A dynamic version can be obtained by replacing $G_{t,k}(\nu )$ in the EWMLA description with
\begin{eqnarray*}
H_{\nu, \tau} \left( \bar{p}_{t,k}\right),
\end{eqnarray*}
where $H_{\nu, \tau}$ is the cumulative distribution function of the Beta distribution and $\bar{p}_{t,k}$ is the average probability forecast defined under EWMA. The tuning parameters $(\alpha, \nu, \tau)$ are learned from the training set by
\begin{eqnarray*}
(\hat{\alpha}, \hat{\nu}, \hat{\tau}) &=& \argmin_{\nu, \tau > 0\ \alpha \in [0,1]} \sum_{k \in S_{train}} \sum_{t=1}^{T_k} \left(Z_k - \hat{p}_{t,k}(\alpha, \nu, \tau)\right)^2
\end{eqnarray*}

@@

Table \ref{prediction} summarizes different ways to aggregate these scores. The first option, denoted by \textit{Scores by Day}, weighs each question by the number of days the question remained open. This is performed by computing the average of the 17,475 scores. The second option, denoted by \textit{Scores by Problem}, gives each question an equal weight regardless how long the question remained open. This is done by first averaging the scores within a question, and then averaging the average scores across all the questions. Both scores can be further broken down into subcategories by considering the length of the questions. The final three columns of Table \ref{prediction} divide the questions into \textit{Short} questions (30 days or fewer), \textit{Medium} questions (between 31 and 59 days), and \textit{Long} Problems (60 days or more). The number of questions in these subcategories were 36, 32 and 98, respectively. The bolded scores indicate the lowest score in each column. The values in the parenthesis quantify the variability in the scores. Under \textit{Scores by Day} the values give the standard errors of all the scores. Under \textit{Scores by Problem}, on other hand, the values represent the standard errors of the average scores of the different questions.

\begin{table}[htbp]
   \centering
      \begin{tabular}{l llll} % Column formatting, @{} suppresses leading/trailing space
 \multicolumn{5}{ c }{Scores by Day}\\
Model & \multicolumn{1}{ c }{All} & \multicolumn{1}{ c }{Short} & \multicolumn{1}{ c }{Medium} & \multicolumn{1}{ c }{Long}\\ \hline
SDLM & 0.100 (0.156) & 0.066 (0.116) & 0.098 (0.154) & 0.102 (0.157)\\ 
BSTC-Log & 0.097 (0.213) & \textbf{0.053} (0.147) & 0.100 (0.215) & 0.098 (0.215)\\ 
STC-Bri & 0.096 (0.190) & 0.056 (0.134) & 0.097 (0.190) & 0.098 (0.192)\\ 
STC-Log & \textbf{0.096} (0.191) & 0.056 (0.134) & \textbf{0.096} (0.189) & \textbf{0.098} (0.193)\\ 
EWMBA & 0.102 (0.203) & 0.060 (0.124) & 0.110 (0.201) & 0.103 (0.206)\\ 
EWMLA & 0.102 (0.199) & 0.061 (0.130) & 0.111 (0.214) & 0.103 (0.200)\\ 
EWMA & 0.111 (0.142) & 0.089 (0.100) & 0.111 (0.136) & 0.112 (0.144)\\ 
&&&&\\
\multicolumn{5}{ c }{Scores by Problem}\\
Model & \multicolumn{1}{ c }{All} & \multicolumn{1}{ c }{Short} & \multicolumn{1}{ c }{Medium} & \multicolumn{1}{ c }{Long}\\ \hline
SDLM & 0.089 (0.116) & 0.064 (0.085) & 0.106 (0.141) & 0.092 (0.117)\\ 
BSTC-Log & 0.083 (0.160) & \textbf{0.052} (0.103) & 0.110 (0.198) & 0.085 (0.162)\\ 
STC-Bri & 0.083 (0.142) & 0.055 (0.096) & 0.106 (0.174) & 0.085 (0.144)\\ 
STC-Log & \textbf{0.082} (0.142) & 0.055 (0.096) & \textbf{0.105} (0.174) & \textbf{0.085} (0.144)\\ 
EWMBA & 0.090 (0.156) & 0.063 (0.101) & 0.118 (0.186) & 0.091 (0.161)\\ 
EWMLA & 0.090 (0.159) & 0.064 (0.109) & 0.120 (0.200) & 0.090 (0.159)\\ 
EWMA & 0.104 (0.105) & 0.092 (0.081) & 0.119 (0.125) & 0.103 (0.107)\\ 
   \end{tabular}
   \caption{Brier Scores based on 10-fold cross-validation. \textit{Scores by Day} weighs a question by the number of days the question remained open. \textit{Scores by Problem} gives each question an equal weight regardless how long the question remained open. The bolded values indicate the lowest scores in each column. The values in the parenthesis represent standard errors in the scores. }
   \label{prediction}
\end{table}

Overall, STC-Bri and STC-Log achieve the lowest average scores across all columns except \textit{Short} where they are slightly outperformed by BSTC-Log.  BSTC-Log, however, turns out to be overconfident (see Section \ref{calibration}). This means that BSTC-Log underestimates the uncertainty in the events and outputs probability forecasts that are typically too near 0.0 or 1.0. As a result, the aggregate forecasts are either very close to the correct answer or very far from it.  As can be seen in Table \ref{prediction}, this results into highly variable forecasting performance. The short questions, however, involve very little uncertainty and were generally the easiest to forecast. On such easy questions, overconfidence can pay off frequently enough to compensate for a few large scores arising from the overconfident and incorrect forecasts.

In comparison to BSTC-Log, the baseline SDLM-model lacks sharpness and is highly under-confident (see Section \ref{calibration}). This behavior is expected as the experts are under-confident at the group-level (see Section \ref{ExpertBias}) and the SDLM-procedure does not use the training set to explicitly calibrate its forecasts. Instead, it merely smooths the forecasts given by the experts. The resulting aggregate forecasts are therefore necessarily conservative and result into high average scores with low variability.

 Similarly behavior is exhibited by EWMA that performs the worst of all the competing models. The other two exponentially weighted aggregators, namely EWMLA and EWMBA, on other hand, make efficient use of the training set and present good forecasting performance in most columns of Table \ref{prediction}. Recall that EWMBA uses the cumulative distribution function of the Beta distribution to transform the average forecast probability. This transformation depends on two parameters and is more flexible than the transformation used by EWMLA. On other hand, only EWLMA is given access to the self-reported expertise information. Based on the results, however, it is unable to use this information to outperform EWMBA. Overall, these two aggregators perform very similarly. They both suffer from over-confidence and are hence unable to outperform the \textit{Sample-Then-Calibrate}-procedure.

%The dataset contained a few long questions with an abrupt change of the crowd belief from one answer option to another. Since these abrupt changes happened generally towards the end of each question, during most days the Brier scores were really high. Given that these problems were typically very long, they gained a higher weight under \textit{Scores by Day} than under \textit{Scores by Problem}. This explains why the \textit{Scores by Day} are higher than the \textit{Scores by Problem} under the columns \textit{All Problems} and \textit{Long}.

\subsection{In- and Out-of-Sample Sharpness and Calibration}
\label{calibration}
A calibration plot is a simple tool for assessing the sharpness and calibration of a model. The idea is to plot the probability forecasts against the observed empirical frequencies. Any deviation from the diagonal line therefore suggests poor calibration. A model is considered under-confident (or over-confidence) if the points follow an S-shaped (or \reflectbox{S}-shaped) trend. In order to assess sharpness of the model, it is common practice to place a histogram of the given forecasts in the corner of the plot.

@@

The top and bottom rows of Figure \ref{Calibration-Out} present calibration plots for SDLM, STC-Log, STC-Bri, and BSTC-Log under in- and out-of-sample probability estimation, respectively. Each setting is of interest in its own right:  Good in-sample calibration is crucial for model interpretability. In particular, if the estimated crowd belief is well-calibrated, then the elements of the bias vector $\boldsymbol{b}$ can be used to study the amount of under- or over-confidence in the different expertise groups. Good out-of-sample calibration and sharpness, on other hand, are necessary properties in predicting future events with high accuracy.  To guide our assessment, the dashed bands around the diagonal connect the point-wise, Bonferroni-corrected (\citet{bonferroni}) 95\% lower and upper critical values under the null hypothesis of calibration. These have been computed by running the bootstrap technique described in \citet{brocker2007increasing} for 10,000 iterations. The in-sample predictions were obtained by running the models for 10,200 iterations, leading to a final posterior sample of 1,000 observations after thinning and using the first 200 iterations for burn-in. The out-of-sample predictions were given by the 10-fold cross-validation discussed in Section \ref{forecasting}.

Overall, the \textit{Sample-Then-Calibrate}-procedure is sharp and well-calibrated both in- and out-of-sample with only a few points barely falling outside the \textit{point-wise} critical values. Since the calibration does not change drastically from the top to the bottom row, the \textit{Sample-Then-Calibrate}-procedure can be considered to present robustness against over-fitting. This is, however, not the case with BSTC-Log that is well-calibrated in-sample but presents over-confidence out-of-sample. Figures \ref{CalibrationNONEa} and \ref{CalibrationNONEb} serve as baselines by showing the reliability plots for the SDLM-model. Since this model does not perform any explicit calibration, it is not surprising to see most points outside the critical values. The pattern in the deviations suggests drastic under-confidence. Furthermore, the inset histogram reveals drastic lack of sharpness. Therefore the \textit{Sample-Then-Calibrate}-model can be viewed as a well-performing compromise between SDLM and BSTC-Log that avoids over-confidence without being too conservative.
